\documentclass{article}

\usepackage[margin=0.5in]{geometry}
\usepackage{multicol}
\usepackage{siunitx}
\usepackage{amsthm}

\theoremstyle{definition}
\newtheorem*{solution}{Solution}
\title{Polygons Set A}
\author{}
\date{}

\begin{document}
\maketitle

\begin{multicols}{2}
    \begin{enumerate}
        \item In parallelogram $ABCD$, diagonals $AC$ and $BD$ intersect at $E$.
            If $AE = 2x + 9$ and $CE = 5x$, what is the length of diagonal $AC$?
            \begin{solution}
                The diagonals of a parallelogram bisect each other, so the length of $AE$ and $CE$ must be equal.
                Solving for $2x + 9 = 5x$, we get $x = 3$, so $AE = CE = 15$ and $AC = 30$.
            \end{solution}
        \item What is the interior angle measure of a regular $15$-gon?
            Solve using two methods.
            \begin{solution}
                The exterior angle measure is easiest to find: $\frac{360}{15} = 24$, so the interior angle is its supplement $\ang{156}$.
                Alternatively, apply the equation $\frac{180(n - 2)}{n}$ to get the same result.
            \end{solution}
        \item What is the area of a triangle with integral side lengths and a perimeter of $8$ cm?
            \begin{solution}
                Consider the combinations of the integers that add up to $8$: $1 + 1 + 6$, $1 + 2 + 5$, $1 + 3 + 4$, $2 + 2+ 4$, $2 + 3 + 3$.
                According to the Triangle Inequality, only one of these sets of integers can be the lengths of the sides of a triangle: $2, 3$, and $3$.
                The altitude of this isosceles triangle meets the base at a right angle, so we can use the Pythagorean theorem to find the height $3^2 -1^2 = h^2$, so $h = \sqrt{8} = 2\sqrt{2}$ and the area is $1 \cdot 2\sqrt{2} = 2\sqrt{2}$.
            \end{solution}
        \item What is the smallest angle which can be created by connecting three vertices of a regular $36$-gon?
            \begin{solution}
                Draw a circle through the vertices of the $36$-gon.
                By the inscribed angle theorem, the angle formed by connecting three vertices is half of the measure of the arc subtended by the angle.
                We can get the smallest arc by connecting two adjacent point to any other point.
                The arc between two adjacent points on a $36$-gon is $\ang{10}$, so the angle formed is $\ang{5}$.
            \end{solution}
        \item In isosceles triangle $ABC$, $m\angle A = \ang{96}$.
            What is $m\angle B$?
            \begin{solution}
                At $\ang{96}$, $\angle A$ cannot be a base angle of an isosceles triangle, because then there would be another $\ang{96}$ angle and the angle sum would be greater than $\ang{180}$.
                Thus $\angle B$ and $\angle C$ are base angles.
                Their sum is $\ang{180} - \ang{96} = \ang{84}$, so $m\angle B = \ang{42}$.
            \end{solution}
    \end{enumerate}
\end{multicols}
\end{document}
