\documentclass{article}
\usepackage{siunitx}
\DeclareSIUnit{\mile}{mi}
\sisetup{per-mode=symbol}
\title{Variable and Equations Set B}
\author{}
\date{}
\begin{document}
    \maketitle
    \begin{enumerate}
        \item What is the value of $127^2 - 14 \cdot 127 + 49$? Bonus: Solve
        using only simple mental math without writing anything.
        \vspace{3cm}
        \item Twins Miley and Riley leave home at the same time, riding their
        bicycles in opposite directions. Miley goes northbound traveling
        \SI{18}{\mile\per\hour}. After $1$ hour, the twins are $32$ miles apart.
        How fast was Riley traveling in the southbound direction?
        \vspace{3cm}
        \item On a certain standardized test with $50$ problems, $5$ points were
        awarded for each correct answer, and $1$ point was deducted for each
        incorrect answer. Chloe answered all the questions on the test and
        scored a total of $184$ points. How many questions did she answer
        correctly?
        \vspace{3cm}
        \item Two Julias and one Chloe can finish a cup of bubble tea together
        in $10$ seconds. One Julia and three Chloes can finish a cup of bubble
        tea together in $8$ seconds. How long will it take for one Julia and one
        Chloe to finish a cup of bubble tea together? Assume that each person
        drinks bubble tea at a constant rate.
        \vspace{3cm}
        \item Working together, Aiden, Barry, and Cynthia can carry
        \SI{48}{\kilogram}. Barry, Cynthia, and Daniela can carry
        \SI{50}{\kilogram}. Cynthia, Daniela, and Aiden can carry
        \SI{54}{\kilogram}. How many kilograms can two Barrys and one Cynthia
        carry together?
        \vspace{3cm}
    \end{enumerate}
\end{document}
