\documentclass{article}
\title{Algebraic Expressions and Equations Set A}
\author{}
\date{}
\begin{document}
    \maketitle
    \noindent Problems should be solved without calculators unless otherwise
    specified. Remember to explain how you solved a problem.
    \begin{enumerate}
        \item In a far-off land, three fish can be traded for two loaves of
        bread and a loaf of bread can be traded for four bags of rice. How many
        bags of rice is one fish worth?
        \vspace{3cm}
        \item The number $66$ is written as the sum of two smaller numbers. One
        of these numbers is $3$ more than twice the other number. Find the
        larger of the two numbers.
        \vspace{3cm}
        \item Cedric began peeling a pile of $44$ potatoes at a rate of $3$
        potatoes per minute. Four minutes later Daniel joined him and peeled at
        a rate of $5$ potatoes per minute. Whey they finished, how many potatoes
        had Daniel peeled?
        \vspace{3cm}
        \item \begin{enumerate}
            \item The sum of two numbers is $7$ and their product is $12$. What
            is twice the sum of their reciprocals? Express your answer as a
            common fraction.
            \vspace{3cm}
            \item The sum of two numbers is $11$ and their product is $13$. What
            is twice the sum of their reciprocals? Express your answer as a
            common fraction.
            \vspace{3cm}
        \end{enumerate}
        \item Cedric and Julia are having a violin practicing battle. They
        practice $5$ hours on the first day, $6$ hours on the second day, $7$
        hours on the third day, and so on. Let $x$ be the number of hours they
        practiced on the last day. Express the number of days in the battle in
        terms of $x$. In other words, find an expression containing $x$ such
        that the value of the expression is the number of days in the battle.
        \vspace{3cm}
    \end{enumerate}
\end{document}