\documentclass{article}
\usepackage[inline]{enumitem}
\title{Algebraic Expressions and Equations Set B}
\author{}
\date{}
\begin{document}
    \maketitle
    \noindent Problems should be solved without calculators unless otherwise specified. Remember to explain how you solved a problem.
    \begin{enumerate}
        \item Donny has two part-time jobs. He earns $\$12$ per hour tutoring, and he earns $\$20$ per hour baby-sitting. Donny would like to work a combination of hours at both jobs to earn exactly $\$360$. If he works at least one hour at each job, with no partial hours worked at either job, what is the difference between the maximum and minimum total hours that Donny can work to earn that amount?
        \vspace{3cm}
        \item A rectangular garden $60$ feet long and $20$ feet wide is enclosed by a fence. To make the garden larger, while using the same fence, its shape is changed to a square. By how many square feet does this enlarge the garden?
        \vspace{3cm}
        \item The average (mean) age of the $40$ members of a computer science camp is $17$ years. There are $20$ girls, $15$ boys, and $5$ adults. If the average age of the girls is $15$ and the average age of the boys is $16$, what is the average age of the adults?
        \vspace{3cm}
        \item On a twenty-question test, each correct answer is worth $5$ points, each unanswered question is worth $1$ point and each incorrect answer is worth $0$ points. Which of the following scores is NOT possible?
        \begin{enumerate*}
            \item $90$ \item $91$ \item $92$ \item $95$ \item $97$
        \end{enumerate*}
        \vspace{3cm}
        \item Find two numbers which differ by $2$ such that $\frac{1}{3}$ of the smaller number plus twice the larger number equals $7$ more than the sum of the two numbers.
        \vspace{3cm}
    \end{enumerate}
\end{document}