\documentclass{article}
\title{Fractions, Ratios, and Proportional Reasoning Set A}
\author{}
\date{}
\begin{document}
    \maketitle
    \noindent Problems should be solved without calculators unless otherwise specified. Remember to explain how you solved a problem.
    \begin{enumerate}
        \item A shop owner increased the price of a jacket by $17\%$. What percent of the new price is the original price of the jacket? Express your answer to the nearest tenth.
        \vspace{3cm}
        \item A single portion of a special concoction is a mixture of $3$ units of ingredient A, $5$ units of ingredient B, and $11$ units of ingredient C. If Isabella wants to make $90$ portions, how many more units of ingredient C does she need than ingredient B?
        \vspace{3cm}
        \item Kathleen has a pattern to knit a scarf that requires $441$ yards of yarn. For this particular pattern, each stitch uses $0.9$ inches of yarn, each row contains $41$ stitches and each full row of knitting contributes $\frac{1}{5}$ inches of length to the scarf. How many inches long will her scarf be when completed? Express your answer to the nearest whole number.
        \vspace{3cm}
        \item If $x$ and $y$ are inversely proportional and $x = 10$ when $y = 6$, what is $x$ when $y = 4$?
        \vspace{3cm}
        \item If $2$ liters of a $20\%$ acid solution are mixed with $8$ liters of a $50\%$ acid solution, what is the concentration of the resulting solution?
        \vspace{3cm}
    \end{enumerate}
\end{document}