\documentclass{article}

\title{Sequences, Series and Patterns Set B}
\date{}
\author{}

\begin{document}
    \maketitle
    \noindent Problems should be solved without calculators unless otherwise
    specified. Remember to explain how you solved a problem.
    \begin{enumerate}
        \item The fourth term of an arithmetic sequence is $3$, and the ninth
        term is $23$. What is the first term of this sequence?
        \vspace{3cm}
        \item Once upon a time, Carl and Steve played a game of ping pong. Carl
        lost, and he was very salty. He wanted to be better than Steve at
        something, so he challenged Steve to solve a math problem. Steve was too
        lazy, so Carl said that he would give Steve $\$25$ if he could compute
        the total distance which a ping pong ball dropped from a height of $10$
        meters will travel, assuming that ping pong balls always bounce up to
        $\frac{2}{3}$ of the height from which they fell. Steve is very bad at
        math but he really wants $\$25$ to buy Minecraft, so he asked you to
        help him. Help Steve buy Minecraft by solving this problem for him.
        Hint: Count the initial fall separately. After the first bounce, the
        ball will rise to $10\left(\frac{2}{3}\right)$ meters before falling back
        down. After the second bounce, the ball will rise up to
        $10\left(\frac{2}{3}\right)^2$ meters before falling back down. This
        continues forever.
        \vspace{3cm}
        \item A fable says that a wise woman solved a king's dire problem, and
        the king said she could have anything she wanted in return. She demurely
        asked only for a chessboard with $1$ grain of wheat on the first square,
        $2$ on the second, $4$ on the third, $8$ on the fourth, and so on up to
        the sixty-fourth square.
        \begin{enumerate}
            \item How many grains of wheat did the wise woman ask for? For your
            convenience, $2^{64} = 18446744073709551616$.
            \vspace{3cm}
            \item How many grains would she have if the number of grains on each
            square is $1, 2, 3, 4, \dots$, instead of $1, 2, 4, 8, \dots$?
            \vspace{3cm}
        \end{enumerate}
        \item The movies in the Revengers series have been coming out every
        three years. The sum of the years in which the first six movies came out
        is $12057$. In what year will the seventh movie come out if the pattern
        continues?
        \vspace{3cm}
        \item A bucket initially has $5$ milliliters of water. Every day, Emily
        removes half of the water, and then Katie adds $5$ milliliters of water.
        Write a formula for the number of milliliters of water in the bucket
        after $x$ days. Hint: After the first day, the amount of water in the
        bucket is $5 \cdot \frac{1}{2} + 5$. After the second day, the amount of
        water in the bucket is $\left(5 \cdot \frac{1}{2} + 5\right)\frac{1}{2}
        + 5 = 5\left(\frac{1}{2}\right)^2 + 5 \cdot \frac{1}{2} + 5$
        milliliters. After the third day, the amount of water in the bucket is
        $\left(\left(5 \cdot \frac{1}{2} + 5\right)\frac{1}{2} +
        5\right)\frac{1}{2} + 5 = 5\left(\frac{1}{2}\right)^3 +
        5\left(\frac{1}{2}\right)^2 + 5 \cdot \frac{1}{2} + 5$.
        \vspace{3cm}
    \end{enumerate}
\end{document}
