\documentclass[twocolumn]{article}

\usepackage[margin=0.5in]{geometry}
\usepackage{flushend}
\usepackage{enumitem}

\title{2.1 Notes}
\author{}
\date{}

\begin{document}
	\maketitle
	
	\section*{Key Concepts}

	\subsection*{Statistics}
	
	\subsubsection*{Mean}
	The \textbf{mean} of a set of numbers is their sum divided by the number of
	numbers. For example, the mean of $1$, $2$, and $3$ is $\frac{1 + 2 + 3}{3}
	= 2$. A useful property of the mean is that the product of the mean and the
	number of numbers is the sum.

	\subsubsection*{Median}
	To find the \textbf{median} of a set of numbers, first list them in
	non-decreasing order. If there are an odd number of numbers, the median is
	simply the number in the middle. If there are an even number of numbers, the
	median is the average (mean) of the two numbers in the middle. For example,
	the median of $1$, $3$, $8$, and $9$ is $\frac{3 + 8}{2} = \frac{11}{2}$ and
	the median of $5$, $8$, $1$, $2$, and $7$ is $5$.

	\subsubsection*{Mode}
	The \textbf{mode} of a set of numbers is the most frequent number, if this
	number is unique. The mode of $1$, $3$, $3$, $4$, $5$, $5$, $5$, and $6$, is
	$5$.

	\subsubsection*{Range}
	The \textbf{range} is simply the absolute difference between the minimum
	number and the maximum number.

	\subsection*{Probability}
	In the context of probability, an \textbf{experiment} is a process that
	produces a random outcome, such as a coin toss or a dice roll. The
	\textbf{sample space} is the set of possible outcomes, such as $\{\, 1, 2,
	3, 4, 5, 6 \,\}$ in the case of a dice roll. An \textbf{event} is a property
	of a subset of the \textbf{sample space}. An event for a dice roll could be
	that the result is even, or that the result is less than $3$ for example. An
	event is said to occur if the outcome has that property.

	The \textbf{probability} of an event or outcome is a real number between $0$
	and $1$ which describes how likely it is to occur. The greater the
	probability, the more likely it is for an event to occur. An event with a
	probability of $0$ never occurs and an evert with a probability of $1$
	always occurs. You can think of the probability as the average frequency of
	an event. An event with a probability of $\frac{1}{2}$ occurs one in two
	times on average, and an event with a probability of $\frac{3}{4}$ occurs
	three in four times on average. The probability of an event $E$ is written
	as $P(E)$. The probability of all the outcomes in a sample space always add
	up to $1$. The probability of an event is the sum of the probabilities of
	the outcomes which it includes. When the outcomes of an experiment are all
	equally likely, this is equal to the number of outcomes in that event
	divided by the total number of possible outcomes. The probability of a dice
	roll resulting in a number less than $5$ is $\frac{2}{3}$, because the
	outcomes are equally likely, there are $4$ outcomes less than $5$, and there
	are $6$ total possible outcomes.

	\subsubsection*{Compound Events}
	The \textbf{complement} of an event is the opposite of it. The complement of
	an event $E$ occurs when $E$ doesn't occur. Going back to the dice roll
	example, the complement of ``less than $5$'' is ``greater than or equal to
	$5$'' and the complement of ``odd'' is ``even''.

	Given two events $E_1$ and $E_2$, their \textbf{union} is defined as ``$E_1$
	or $E_2$''. That is, the union of $E_1$ and $E_2$ occurs if either $E_1$,
	$E_2$, or both, occur. This definition extends to more than two events.  In
	a dice roll, the union of the events ``even'' and ``less than $5$'' is
	``even or less than $5$'', which includes anything other than $5$.

	The union of $E_1$ and $E_2$ is written as $E_1 \cup E_2$. The
	\textbf{intersection} of events $E_1$ and $E_2$ is the event that both $E_1$
	and $E_2$ occur. The intersection of $E_1$ and $E_2$ is written as $E_1 \cap
	E_2$.

	\subsubsection*{Independent Events}
	Two events are said to be \textbf{independent} if knowing the outcome of one
	of the events does not affect the outcome of the other event. If I first
	flip a coin and then roll a die, knowing that the coin flip resulted in
	heads doesn't change the probability that the dice roll will result in an
	odd number, so these events are independent. The event of a dice roll
	resulting in a number greater than or equal to $3$ is not independent from
	the event of the same dice roll resulting in a number greater than or equal
	to $4$, because if we know that it is greater than or equal to $3$, it's
	more likely to be greater than or equal to $4$. Note that events from
	separate processes are always independent, but independent events are not
	necessarily from separate processes. For example, the event that a dice roll
	results in an even number is independent from the event that the same dice
	roll results in a number less than $4$.

	When two events are independent, the probability of their intersection is
	the product of their probabilities. That is, if $E_1$ and $E_2$ are
	independent, $P(E_1 \cap E_2) = P(E_1)P(E_2)$. The probability of the union
	of two events is the sum of their probabilities minus the probability of
	their intersection. In other words, $P(E_1 \cup E_2) = P(E_1) + P(E_2) -
	P(E_1 \cap E_2)$.

	\section*{Problems}

	\subsection*{Statistics}
	\begin{enumerate}
		\item Find the mode, median, arithmetic mean, range, and geometric mean
			of the following numbers: $2, 4, 4, 5, 6, 10$.
			\vspace{3cm}
		\item Two numbers $x$ and $y$ have a geometric mean of $12$ and an
			arithmetic mean of $12.5$. Find $x^2 + y^2$.
			\vspace{3cm}
		\item A student has an average score of $80$ on her first four tests.
			What must she score on the next test to raise her average to $82$?
			\vspace{3cm}
		\item The arithmetic mean of $12$ scores is $82$. When the highest and
			lowest scores are removed, the new mean becomes $84$. If the highest
			of the $12$ scores is $98$, what is the lowest score?
			\vspace{3cm}
		\item What is the average of seven numbers if the average of the first
			two is $9$ and the average of the last $5$ is $16$?
			\vspace{3cm}
	\end{enumerate}

	\subsection*{Probability}
	\begin{enumerate}[resume]
		\item A box contains three red balls and three green balls. Two balls
			are chosen.
			\begin{enumerate}
				\item What is the probability that a red ball is chosen first,
					then a green ball?
					\vspace{3cm}
				\item What is the probability that one red ball and one green
					ball are chosen?
					\vspace{3cm}
			\end{enumerate}
		\item John and Jayne each choose an integer from $1$ to $10$ inclusive.
			What is the probability that they each pick a number greater than
			$7$?
			\vspace{3cm}
		\item If Saphira randomly chooses a $4$-digit number, what is the
			probability that all four digits will be distinct?
			\vspace{3cm}
		\item A Flo Hyman spike puts the ball away $60\%$ of the time. What is
			the probability that the first spike on a given point is returned
			and the second is not?
			\vspace{3cm}
	\end{enumerate}
\end{document}
