\documentclass{article}

\usepackage[group-separator={,}]{siunitx}

\title{Counting Set B}
\author{}
\date{}

\begin{document}
\maketitle
\noindent Problems should be solved without calculators unless otherwise 
specified.  Remember to explain how you solved a problem.
\begin{enumerate}
    \item A 24-hour digital clock displays times from 00:00 to 23:59. How 
        many of the times displayed on this clock contain the digit 2?
        \vspace{3cm}
    \item Jeremy owns a rectangular plot of land that is $60$ yards long and 
        $30$ yards wide.
        \begin{enumerate}
            \item If he places a fence post at each corner and posts are placed 
                every three yards, how many fence posts will there be on each 
                side?
                \vspace{3cm}
            \item If he places a fence post at each corner and posts are placed 
                every three yards, how many fence posts will he need to enclose 
                his land?
                \vspace{3cm}
        \end{enumerate}
        \vspace{3cm}
    \item How many distinct pairs of consecutive integers have a product 
        less than \num{10000}?
        \vspace{3cm}
    \item Tom randomly selects three different numbers from the set $\{1, 2, 
        3, 4\}$.  Jerry randomly selects one number from the set $\{2, 4, 6, 
        8 ,10, 12\}$. What is the probability that Jerry's number is greater 
        than the sum of Tom's numbers? Express your answer as a common 
        fraction.
        \vspace{3cm}
    \item All squares are both rectangles and rhombuses. All rhombuses and 
        rectangles are parallelograms. On a sheet of paper, Josh draws $19$ 
        rectangles, $15$ rhombuses, and $7$ squares. How many parallelograms 
        did Josh draw?
        \vspace{3cm}
\end{enumerate}
\end{document}
