\documentclass{article}
\usepackage{amsthm}

\theoremstyle{definition}
\newtheorem*{solution}{Solution}

\title{Combinatorics Set A}
\author{}
\date{}

\begin{document}
    \maketitle
    \noindent Problems should be solved without calculators unless otherwise specified.
    Remember to explain how you solved a problem.
    \begin{enumerate}
        \item In how many different ways can a student guess a complete set of answers to a
        five-item true/false quiz?
        \begin{solution}
            For each question there are $2$ choices, so for all five there are $2^5 = 32$ choices.
        \end{solution}
        \item How many ways can $5$ books be arranged on a shelf if $2$ of the books must
        remain together?
        \begin{solution}
            The key here is to realize that the books which must be together may be treated as a
            single unit. Within that unit, the books may be in $2$ different orders (AB or BA) but
            we can account for that by simply multiplying by $2$ at the end. We thus have $4$ books
            (one is our two-book unit) and these can be arranged in $4! = 24$ ways. Multiplying by
            $2$ then yields $48$. (Make sure in your mind that all configurations are counted, and
            that none are counted twice!)
        \end{solution}
        \item If $n = 100$, find the value of $\frac{(n+1)!}{(n-1)!}$
        \begin{solution}
            We are asked to evaluate $\frac{101!}{99!}$. Remember that $101! = 101 \cdot 100 \cdot
            99!$, so $\frac{101!}{99!} = 101 \cdot 100 = 10100$.
        \end{solution}
        \item Andrew and Lindsey are seated at a round table with four other people. If everyone
        is randomly seated, what is the probability that Andrew and Lindsey are seated next to
        each other? Express your answer as a common fraction.
        \begin{solution}
            If these six people were standing in a line, then there would be $6! = 6 \cdot 5 \cdot
            4 \cdot 3 \cdot 2 \cdot 1 = 720$ orders. Since this is a round table, these same
            arrangements of people can be rotated in $6$ different places, so there would seem to
            be only $720 \div 6 = 120$ seating arrangements. Since we are interested in seating
            arrangements with Andrew and Lindsey seated together, let's imagine that Andrew and
            Lindsey are stuck together and act as a single person. Then we have the same situation
            with five people, so there are $5! \div 5 = 120 \div 5 = 24$ seating arrangements.
            However, we can glue Andrew and Lindsey together in $2$ different ways, so there are
            actually $2 \cdot 24 = 48$ seating arrangements with Andrew and Lindsey seated together.
            Therefore, the probability that they are seated together is $\frac{48}{120} = \frac{2}{5}$.
        \end{solution}
        \item What is the probability of getting exactly $6$ correctly answers on a 10-question
        true-false test by randomly guessing? Express your answer as a common fraction.
        \begin{solution}
            Each of the $10$ questions will be either true or false, so there are $2^{10} = 1024$
            possible combinations of answers for the test. There are "10 choose 6" or ${10 \choose 6}
            = \frac{10!}{4! \cdot 6!} = \frac{10 \cdot 9 \cdot 8 \cdot 7}{4 \cdot 3 \cdot 2 \cdot 1}
            = 10 \cdot 3 \cdot 7= 210$ ways to get exactly $6$ correct answers. So, the probability
            is $\frac{210}{1024} = \frac{105}{512}$.
        \end{solution}
    \end{enumerate}
\end{document}