\documentclass[twocolumn]{article}

\usepackage[margin=0.5in]{geometry}
\usepackage{flushend}
\usepackage{amsthm}
\usepackage{amsmath}

\theoremstyle{definition}
\newtheorem*{solution}{Solution}
\title{More Combinatorics Set B}
\author{}
\date{}

\begin{document}
    \maketitle
    \begin{enumerate}
        \item Andrew and Lindsey are seated at a round table with four other people.
        If everyone is randomly seated, what is the probability that Andrew and 
        Lindsey are seated next to each other? Express your answer as a common 
        fraction.
        \begin{solution}
            If these six people were standing in a line, then there would be $6!  
            = 6 \cdot 5 \cdot 4 \cdot 3 \cdot 2 \cdot 1 = 720$ orders. Since 
            this is a round table, these same arrangements of people can be 
            rotated in $6$ different places, so there would seem to be only 
            $\frac{720}{6} = 120$ seating arrangements. Since we are interested 
            in seating arrangements with Andrew and Lindsey seated together, 
            let's imagine that Andrew and Lindsey are stuck together and act as 
            a single person. Then we have the same situation with five people, 
            so there are $\frac{5!}{5} = \frac{120}{5}  = 24$ seating 
            arrangements.  However, we can glue Andrew and Lindsey together in 
            $2$ different ways, so there are actually $2 \cdot 24 = 48$ seating 
            arrangements with Andrew and Lindsey seated together.  Therefore, 
            the probability that they are seated together is $\frac{48}{120} = 
            \frac{2}{5}$.
        \end{solution}
        \item In how many ways can Antoinette give one M\&M each to two children. If she 
        has $3$ different red, $4$ different brown, and $5$ different tan ones and two
        children insist upon having M\&Ms of different colors?
        \begin{solution}
            We can separate individual cases, find the number of ways for each, and then
            add them up. In this problem there are $6$ cases: red-brown, brown-red,
            red-tan, tan-red, brown-tan, tan-brown. For each red-brown we have $3 \cdot 4
            = 12$ ways (and the same for brown-red), for red-tan $3 \cdot 5 = 15$ ways
            (same for tan-red), and for brown-tan $4 \cdot 5 = 20$ ways (same for
            tan-brown). The total is $2(12 + 15 + 20) = 94$.
        \end{solution}
        \item Palindromes, like $23432$, read the same forward and backward. Find the sum
        of all four digit positive integer palindromes. (Hint: What is the sum of the
        first and last four digit palindrome added together?)
        \begin{solution}
            Suppose we list all the palindromes: $\{1001, 1111, 1221, \dots, 9889, 9999\}$.
            Notice that if we add the first and the last, we get $11000$. The same holds
            if we add the second and the next-to-last and so on. Each such pair always sums
            to $11000$. So how many pairs are there? There are ten palindromes starting with
            each digit from $1$ to $9$, so there are $90$ palindromes. Hence, there are $45$
            pairs and our desired sum is $45 \cdot 11000 = 495000$.
        \end{solution}
        \item How many of the arrangements of the letters in the word COUNTING contain
        a double-N?
        \begin{solution}
            The restriction requires that the N's be grouped together, so we do just that:
            treat them as a single letter. There are $7$ letters so we get $^7P_7 = 7! = 
            5040$.
        \end{solution}
        \item The $54$-member Council for Security and Cooperation in Europe wishes to 
        choose $3$ member states for different leadership positions. The L lobby decrees that 
        at least one of Lithuania, Lichtenstein, Latvia, and Luxembourg must be chosen. In 
        how many ways can the committee be selected?
        \begin{solution}
            The simplest approach is to count the number of choices of the offices
            \emph{without} choosing any of the L countries. Then there are $50$ states and
            $3$ different positions, making $50 \cdot 49 \cdot 48$ choices. We wish to
            subtract the number of committees which can be formed without restriction, or
            $54 \cdot 53 \cdot 52$. The committees left are those which satisfy the L lobby.
            The result is just $54 \cdot 53 \cdot 52 - 50 \cdot 49 \cdot 48 = 31224$.
        \end{solution}
    \end{enumerate}
\end{document}
