\documentclass[twocolumn]{article}

\usepackage[margin=0.5in]{geometry}
\usepackage{flushend}
\usepackage{amsthm}
\usepackage{amsmath}

\theoremstyle{definition}
\newtheorem*{solution}{Solution}

\title{More Combinatorics Set A}
\date{}
\author{}

\begin{document}
\maketitle
\begin{enumerate}
    \item In how many ways can a five letter ``word'' be written using only the 
        first half of the alphabet with no repetitions such that the third and 
        fifth letters are vowels and the first letter is a consonant?
        \begin{solution}
            There are three vowels and ten consonants in the first half of the 
            alphabet. Following the strategy of counting the position with the 
            most restrictions first, we'll first count the number of ways to 
            choose the letters in the first, third, and fifth positions and then 
            count the number of ways to choose the letters in the second and 
            fourth positions. There are $10$ ways to choose the first letter and 
            $3$ ways to choose the third letter. Note that we don't have to 
            worry about the two letters being the same because one is a 
            consonant and the other is a vowel. Next, there are $2$ ways to 
            choose the fifth letter since we can't repeat the third letter. 
            There are $10$ ways to choose the second letter since there are $13$ 
            letters in the first half of the alphabet and $3$ of them are 
            already used. Similarly, there are $9$ ways to choose the fourth 
            letter. Therefore, the total is $10 \cdot 3 \cdot 2 \cdot 10 \cdot 9 
            = 5400$.
        \end{solution}
    \item In how many ways can the letters SEANCHEN be rearranged?
        \begin{solution}
            There are $8$ letters in total. There are two E's and two N's, and 
            all the other letters are unique. There are $8!$ ways to arrange $8$ 
            distinct things. If we considered the two E's and the two N's to be 
            unique, then there would be $2$ ways to order the E's and $2$ ways 
            to order the N's. Since reordering the E's and the N's doesn't 
            actually change anything, the number of arrangements where all the 
            letters are unique is $2! \cdot 2! = 4$ times the number of 
            arrangements that we want to count. Therefore, there are 
            $\frac{8!}{4} = 10080$ ways to arrange the letters SEANCHEN.
        \end{solution}
    \item At the end of a professional bowling tournament, the top $5$ bowlers have a 
        playoff. First \#$5$ bowls \#$4$. The loser receives fifth prize and the winner 
        bowls \#$3$ in another game. The loser of this game receives fourth prize and the 
        winner bowls \#$2$. The loser of this game receives third prize and the winner bowls 
        \#$1$. The winner of this game gets first prize and the loser gets second prize. 
        In how many orders can bowlers \#$1$ through \#$5$ receive the prizes?
        \begin{solution}
            There are four games. We might hypothesize that every sequence of 
            outcomes for the four games result in a different prize order. To 
            prove this, imagine changing the outcome for some of the games. No 
            matter how we change the outcomes, there will always be at least one 
            bowler who gets a higher prize than before, so the order of the 
            prizes must be different. Since each sequence of outcomes result in 
            a different prize order, the number of possible prize orders is 
            equal to the number of possible outcome sequences, which is $2^4 = 
            16$.
        \end{solution}
    \item In how many ways can the letters in the word MINIMIZATION be arranged 
        such that no two vowels are consecutive?
        \begin{solution}
            Notice that exactly half of the letters are vowels. First, we'll 
            choose the positions for the vowels. It's easy to see that there are 
            $7$ ways to choose $6$ non-adjacent positions out of $12$. Now that 
            we have chosen the positions for the vowels and consonants, we can 
            count the number of ways to arrange the vowels and consonants 
            separately. For the vowels, we have one O, four I's, and one A. 
            There are $6$ ways to choose the position of the O, and $5$ ways to 
            choose the position of the A, and the rest must be I's. Therefore, 
            there are $6 \cdot 5 = 30$ ways to order the vowels. For the 
            consonants, we have two N's, two M's, one T, and one Z. There are 
            $6!$ ways to arrange six letters, and we divide by $2! \cdot 2!$ to 
            account for the two pairs of repeated letters. (See the notes for 
            more details on why we do this.) The number of ways to arrange the 
            consonants is then $\frac{6!}{2! \cdot 2!} = 180$.
        \end{solution}
    \item In how many ways can $4$ identical red chips and $2$ identical white chips be 
        arranged in a circle?
        \begin{solution}
            The only thing that matters is the gap between the two white chips. 
            The white chips can be adjacent, have one red chip between them, or 
            have two red chips between them. Therefore there are $3$ 
            arrangements.
        \end{solution}
\end{enumerate}
\end{document}
