\documentclass{article}

\usepackage{ulem}

\title{More Combinatorics Set B}
\author{}
\date{}

\begin{document}
\maketitle
\noindent Problems should be solved without calculators unless otherwise 
specified. Remember to explain how you solved a problem.
\begin{enumerate}
    \item Less than $50$ people are at a party. Each person \sout{shakes hands 
        with} elbow bumps every other person exactly once. If there is an odd 
        number of total elbow bumps at the party, what is the largest number of 
        people that could be at the party.
        \vspace{3cm}
    \item In how many ways can Sean give one M\&M each to two children if he has 
        $3$ different red, $4$ different brown, and $5$ different tan ones and 
        two children insist upon having M\&Ms of different colors?
        \vspace{3cm}
    \item Palindromes, like $23432$, read the same forward and backward. Find 
        the sum of all four digit positive integer palindromes. (Hint: What is 
        the sum of the first and last four digit palindrome added together?)
        \vspace{3cm}
    \item How many of the arrangements of the letters in the word COUNTING 
        contain a double N?
        \vspace{3cm}
    \item The $54$-member Council for Security and Cooperation in Europe wishes 
        to choose $3$ member states for different leadership positions. The L 
        lobby decrees that at least one of Lithuania, Lichtenstein, Latvia, and 
        Luxembourg must be chosen. In how many ways can the committee be 
        selected?
        \vspace{3cm}
\end{enumerate}
\end{document}
