\documentclass{article}

\title{Statistics and Probability Set A}
\date{}
\author{}

\begin{document}
    \maketitle
    \noindent Problems should be solved without calculators unless otherwise
    specified. Remember to explain how you solved a problem.
    \begin{enumerate}
        \item Anwar rolls two dice and adds up the results.
        \begin{enumerate}
            \item Find the probability of rolling a six if two six-sided dice
                are rolled. Hint: Count the number of ways to roll a sum of six
                and divide it by the total number of outcomes for rolling two
                dice.
                \vspace{3cm}
            \item Find the probability of each sum from $2$ to $12$. Try to
                notice a pattern.
                \vspace{3cm}
        \end{enumerate}
        \item There are $3$ blue balls and $4$ red balls in a bag. Chloe
            randomly draws two balls from the bag with replacement, meaning that
            she draws one ball, replaces it, and then draws another ball. What
            is the probability that one of them is red and the other one is
            blue?
            \vspace{3cm}
        \item Alastair's favorite book series has seven books containing $223$,
            $251$, $317$, $636$, $766$, $607$, and $607$ pages. Montana's
            favorite book series has seven books containing $309$, $341$, $435$,
            $734$, $870$, $652$, and $759$ pages. What is the absolute
            difference between the median number of pages in the books of
            Alastair's and Montana's favorite book series?
            \vspace{3cm}
        \item There are $270$ bats living in a cave on the first day of June.
            Every day in June, some number of bats arrive to join the bats
            already there. At the end of June 30, there are $1000$ bats in the
            cave. On average, how many bats arrived each day in June? Express
            your answer as a decimal to the nearest tenth.
            \vspace{3cm}
        \item A fair coin is flipped four times. What is the probability that it
            lands heads up at least as many times as it lands tails up?
    \end{enumerate}
\end{document}
