\documentclass{article}

\usepackage{amsmath}
\usepackage{hyperref}

\title{Statistics and Probability Set B}
\author{}
\date{}

\begin{document}
\maketitle
\noindent Problems should be solved without calculators unless otherwise
specified.  Remember to explain how you solved a problem.
\begin{enumerate}
    \item Twenty-five students have a combined average of $84$ on a test, while
        another group of twenty students have a combined average of $66$. Find
        the overall average.
        \vspace{3cm}
    \item Three six-sided dice are rolled. What is the probability that at least
        one of them comes up with a $5$ or a $6$? Hint: First find the
        probability that none of them comes up with $5$ or $6$.
        \vspace{3cm}
    \item There is a $20\%$ chance it will rain today. If it rains, there is a
        $10\%$ chance that we will be allowed to go outside; otherwise, there is
        an $80\%$ chance we will be able to go outside. What is the probability
        that we will be able to go outside? Hint: We can go outside if (it rains
        AND we can go outside) OR (it doesn't rain AND we can go outside). Are
        the two events ``it rains AND we can go outside'' and ``it doesn't rain
        AND we can go outside'' mutually exclusive?
        \vspace{3cm}
    \item What is the probability of getting at least $9$ heads when flipping a
        coin $10$ times? Hint: Find the probability of getting exactly $9$ heads
        and the probability of getting $10$ heads.
        \vspace{3cm}
    \item This stem-and-leaf plot shows the heights of the basketball players at
        East High School. If $\begin{array}{r | l} 6 & 8 \end{array}$ represents 
        $68$ inches, what is the average height of the basketball players at 
        East High School? See        
        \url{https://en.wikipedia.org/wiki/Stem-and-leaf_display} if you don't 
        know about stem-and-leaf plots.
        \[
            \begin{array}{r | l}
                6 & 8~8~9~9 \\
                7 & 1~2~7~7~8~8 \\
                8 & 0~1
            \end{array}
        \]
        \vspace{3cm}
\end{enumerate}
\end{document}
