\documentclass{article}

\title{Sequences, Series, and Patterns Set A}
\date{}
\author{}

\begin{document}
    \maketitle
    \noindent Problems should be solved without calculators unless otherwise
    specified. Remember to explain how you solved a problem.
    \begin{enumerate}
        \item What is the value of $k$ in the arithmetic sequence $-13, -7, -1,
        k, 11$?
        \vspace{3cm}
        \item Insert two geometric means between $2$ and $16$.
        \vspace{3cm}
        \item The students from Regent Middle School sat $20$ rows in such a way
        that each row after the first had $3$ more students sitting in it than
        the previous row. If $16$ students sat in the fifth row, how many
        students are there in total?
        \vspace{3cm}
        \item A rectangular lawn is mowed every five days. On each of these
        days, the lawn is mowed in one direction, but the direction varies from
        one mowing to the next in the following order: East-West (E-W),
        Northeast-Southwest (NE-SW), North-South (N-S) and Northwest-Southeast
        (NW-SE). If the lawn is first mowed E-W on Day $1$, on Day $201$ in
        which direction is the lawn mowed, E-W, NE-SW, N-S, or NW-SE?
        \vspace{3cm}
        \item Cara received a rose that has $n$ petals, $\frac{n + 5}{3}$
        leaves, and $\frac{n - 2}{4}$ thorns. The number of petals, leaves, and
        thorns are all numbers in the Fibonacci sequence ($1, 1, 2, 3, 5, 8,
        \dots$, where each term is the sum of the previous two terms), and $n < 100$. How many leaves does Cara's rose have?
        \vspace{3cm}
    \end{enumerate}
\end{document}