\documentclass{article}

\usepackage[margin=0.5in]{geometry}
\usepackage{multicol}

\title{Problem-Solving Set B}
\author{}
\date{}

\begin{document}
\maketitle
\noindent Problems should be solved without a calculator unless otherwise specified.
Remember to explain how you solved a problem.
\begin{multicols}{2}
    \begin{enumerate}
        \item Michelle teaches on Tuesday and Thursday evenings.
            On Tuesdays she makes $\$112.50$, and on Thursdays she makes $\$135$.
            There are $31$ days this month.
            What is the minimum amount that Michelle will earn this month?
            \vspace{3cm}
        \item In a survey of $200$ people, $161$ reported owning a car, $58$ owned a bicycle, and $74$ had a valid mass transit pass.
            A total of $12\%$ of the survey respondents reported owning all three, while $2.5\%$ reported owning none.
            How many of the people surveyed owned exactly one of the three?
            \vspace{3cm}
        \item Armin's $13$th birthday was on Saturday, July 4, 2020.
            How old will Armin be when his birthday next falls on a Saturday?
            \vspace{3cm}
        \item Tonya found $\$2.25$ in nickels and quarters in her sofa cushions.
            If the number of nickels Tonya found is five more than three times the number of quarters she found, what is the total number of coins Tonya found?
            \vspace{3cm}
        \item In how many ways can all the numbers $1$, $2$, $3$, $4$, $5$, $6$ and $7$ be separated into two groups, so that the sum of the numbers in both groups is the same?
            \vspace{3cm}
    \end{enumerate}
\end{multicols}
\end{document}