\documentclass{article}

\usepackage[margin=0.5in]{geometry}
\usepackage{multicol}
\usepackage{siunitx}

\title{Solid Geometry Set A}
\author{}
\date{}

\begin{document}
\maketitle
\noindent Problems should be solved without calculators unless otherwise specified.
Remember to explain how you solved a problem.
\begin{multicols}{2}
    \begin{enumerate}
        \item A right circular cone with base radius $\SI{4}{cm}$ has surface area $\SI{56\pi}{cm^2}$.
        What is the height of the cone?
        Express your answer in simplest radical form.
        \vspace{3cm}
        \item What is the greatest distance between any two vertices of a rectangular prism with dimensions $\SI{8}{cm}$ by $\SI{9}{cm}$ by $\SI{12}{cm}$?
        \vspace{3cm}
        \item What is the number of solid $3$-inch by $2$-inch by $2$-inch rectangular prisms that can be arranged to form a solid cube of edge length $1$ foot?
        \vspace{3cm}
        \columnbreak
        \item A cylindrical container holds $20$ fluid ounces.
        It has a radius of $3$ inches and a height of $12$ inches.
        How many fluid ounces will a similar container with a radius of $4.5$ inches hold?
        Express your answer as a decimal to the nearest tenth.
        \vspace{3cm}
        \item Keaton wants to build a rectangular prism with volume $\SI{2016}{in^2}$ so that the length of each edge is a whole number of inches.
        What is the least possible sum of the three dimensions of the prism he builds?
        \vspace{3cm}
    \end{enumerate}
\end{multicols}
\end{document}
